Understanding the Socio-Economic Determinants of Voter Behavior: An Analysis of the 2020 U.S. Presidential Election

### 2024-03-12 paper/us_election_2020.qmd
change

@@

@fig-modelresults1 (see @sec-credibility-interval) inshows range of coefficient estimates of our model within the 90% probability. Due to the fact that the credibility interval for race "Other" is particularly large, we cannot observe the trend of the 90% credibility intervals of other variables. Therefore we created figure # with the x axis limited from -10 to 10.

Combing @fig-modelresults1 and @fig-modelresults2, we observe statistical significance for the coefficient estimates for students, the Northeast region, individuals identifying with two or more races, individuals identifying with "Other" racial category, Native Americans, Black individuals, and the intercept, Asians in the Midwest region who are employed full-time. The estimates are significant if the intervals do not cross 0. The value for the estimates are in log-odds, indicating that if the coefficient is positive, the individual supports Biden, if negative, the individual supports Trump.

@@

maybe talk about employment?
tax

@@

## Credibility interval

```{r}
#| label: fig-conf
#| fig-cap: Comparing the posterior with the prior 
#| echo: false
#| warning: false
#| message: false
plot(
  political_preferences1,
  "areas"
)
```
```{r}
#| label: fig-conf_lim
#| fig-cap: Comparing the posterior with the prior 
#| echo: false
#| warning: false
#| message: false
#| 
model_plot <- plot(
  political_preferences1,
  "areas"
)
# Modify the x-axis limits
model_plot + xlim(-10, 10) +  # Adjust the limits as needed
  labs(x = "90% Credibility Interval")
```
## Credibility Interval {#sec-credibility-interval}

@@

modelplot(political_preferences1, conf_level = 0.95, size = 0.1) +
 labs(x = "90% credibility interval")
```

>>>>

## Model Implication
In @fig-post_dist, the great fit of the posterior distribution from our logistic regression model with actual voting data suggests accurate capture of voting patterns. This indicates the accuracy of our model's voting preference prediction to the 2020 election data. Also, @fig-post_prior compares the posterior to the prior, which shows minimal parameter changes except for the parameter "raceOther". The discrepancy for the parameter "raceOther" is not critical due to the low representation of "raceOther" in the dataset.

The trace plot in @fig-mcmc-1 does not suggest anything out of the ordinary. Also, with the Rhat plot (@fig-mcmc-2), we can observe that everything is close to 1, and no more than 1.05.

@@

@fig-modelresults1 (see @sec-credibility-interval) shows range of coefficient estimates of our model within the 90% probability. Due to the fact that the credibility interval for race "Other" is particularly large, we cannot observe the trend of the 90% credibility intervals of other variables. Therefore we created figure # with the x axis limited from -10 to 10.

Combining @fig-modelresults1 and @fig-modelresults2, we observe statistical significance for the coefficient estimates for students, the Northeast region, individuals identifying with two or more races, individuals identifying with "Other" racial category, Native Americans, Black individuals, and the intercept, Asians in the Midwest region who are employed full-time. The estimates are significant if the intervals do not cross 0. The value for the estimates are in log-odds, indicating that if the coefficient is positive, the individual supports Biden, if negative, the individual supports Trump.

@@

will write later

@@

## Credibility Interval {#sec-credibility-interval}

@@

modelplot(political_preferences1, conf_level = 0.90, size = 0.1) +
  labs(x = "90% credibility interval")
```
